\textbf{Three equanimous aspects\\of scale-free networks}\\

### 2015-02-03 essay.tex
alterada estrutura do escrito

\section{Canonical scale-free networks}\label{sec:can}
Networks with a power law distribution of connectivity (degree) are called scale-free. In other words, be $p(k)$ the probability that an arbitrary vertex has degree $k$, than, for a scale-free network, one can assume:
\begin{equation}
p(k) \sim k^{-\gamma}
\end{equation}
\noindent where $\gamma$ is constant and typically $\gamma \in [2,3]$ and $\gamma > 1$ always. This same distribution is called, under certain conditions, the Pareto distribution or the Zipf law.

@@

>>>>

\section{Canonical background}\label{sec:can}
Networks with a power law distribution of connectivity (degree) are called scale-free. In other words, be $p(k)$ the probability that an arbitrary vertex has degree $k$, than, for a scale-free network, one can assume:
\begin{equation}
p(k) \sim k^{-\gamma}
\end{equation}
\noindent where $\gamma$ is constant and typically $\gamma \in [2,3]$ and $\gamma > 1$ always. This same distribution is called, under certain conditions, the Pareto distribution or the Zipf law.

\subsection{Zipf law}
\subsection{Pareto distribution}
\subsection{Scale-free networks}

@@

\section{Exaltation of hubs and delusions of grandeur}\label{sec:delusion}
